\documentclass{article}
\usepackage{xcolor}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\title{\textcolor{blue}{\underline{HomeWork}} }
\author{\textcolor{olive}{\uppercase{mohanad hrebat}}}
\date{\textcolor{magenta}{\textit{April 4, 2024}}}

\begin{document}
\definecolor{mohanad}{RGB}{255, 255, 204} % احضرت الاحداثيات من الانترنت
\definecolor{lighblue}{RGB}{0, 128, 255}
\pagecolor{mohanad}
\fancyfoot[C]{\textcolor{magenta}{Page \thepage}}
\fancyhead[L]{\textcolor{blue}{Homework Assignment}}%اخذته من
\maketitle

\begin{abstract}
  \textcolor{cyan}{This homework assignment covers various LaTeX commands and ele-
ments. Your task is to replicate this document using LaTeX.}  
\end{abstract}

\tableofcontents

\newpage

\section{\textcolor{lighblue}{Introduction}}

This is the introduction section of the homework assignment.

\subsection{Objective}
The objective of this assignment is to familiarize yourself with LaTeX syntax
and commands.

\section{Nested Lists}
design your own nested list

\subsection{Examples}
\begin{enumerate}
    \item item1
     \begin{itemize}
    \item item 1-1
    \end{itemize}
     \begin{enumerate}
        \item item 1-2
    \end{enumerate}
\end{enumerate}

\section{Tasks}
\begin{enumerate}
\item Create a LaTeX document with the provided title, author, and date in-
formation.
\item Add an abstract
\item Include a table of contents.
\item Use different font styles such as bold, italic, and underlined.
\item Create nested lists using itemize and enumerate environments.
\item Change page color and text color using the xcolor package.
\item Use the fancyhdr package to customize headers and footers.
\item Apply different line spacing using the setspace package.
\end{enumerate}

\begin{flushright}
This text is right aligned.
\end{flushright}
\begin{center}
  This text is centered.  
\end{center}

\subsection*{Conclusion}
\addcontentsline{toc}{subsection}{Conclusion}

This concludes the homework assignment.

\section*{Acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}
I would like to thank everyone who contributed to this homework assignment.

\section*{References}
\addcontentsline{toc}{section}{References}
[1] LaTeX Documentation

\end{document}
